Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging Patterns of Queen Bumble Bees

### 2023-03-03 script/conceptual-tables-boxes.rmd
need to check diff, copied in a funny character

---
title: "Conceptual Boxes"
author: "steppe"
date: "2023-03-01"
output: html_document
---

@@

```{r Applications of metabarcoding in plants}

applications <- data.frame(
  'Application' = c(
    'Plant-Animal Interactions',
    'Noxious Weed Detection',
    'Detection of Rare Species', 
    'Forensic Science',
    'Pharmaceutical/Nutraceutical'
  ),
  'Example' = c(

    'Dietary Preferences of herbivores',
    'Presence of species by hydrologic Basin',
    'Presence of Rare Aquatic Species',
    'Identifying the provenance of materials found at crime scene',
    'Identifying adulterants in wholesale products'
  ),
  'Citation' = c(
    'Soininen et al. 2009',
    'Coghlan et al. 2021',
    'Tsukamoto et al. 2021',
    'Allwood et al. 2020',
    'Bell et al. 2022'
  )
)
```

@@

```{r Major Issues}

bottlenecks <- tibble(

  'Issue' = c(
    'Taxonomic Resolution',
    'Reference Library Coverage - Phylogenetic',
    'Reference Library Coverage - Spatial',
    'Reference Library Generation', 
    'Uncertainty with Matches',
    'Species Surrogates',
    'False Positives'
  ),

  'Approach' = c(
    'A353', 
    'Kew PAFTOL, no phylogenetic biases', 
    'Some bias persists towards Europe, North America',
    'Spatial Modelling; Code within', 
    'Temporal Filter System',
    'Temporal Filter System',
    'Spatial & Temporal Modelling, Jaccard Index, high quality reference loci'
  ),

  'Citation' = c(
    c('Coissoc et al. 2016, Kress 2017'),  #taxonomic resolution
    c('Kress 2017, Bell et al. 2022'),  # reference library phylogenetic
    c('Cheng et al. 2018, Darwin Tree of Life 2022, Lewin et al. 2020, Bell et al. 2021'),  # 'Reference Library spatial
    c('Bell et al. 2022'), #  'Reference Library Generation', 
    c('Bell et al. 2022'), #   'Uncertainty with Matches',
    c('?'), #   'Species Surrogates',
    c('Bell et al. 2021') #   'False Positives'
  )

)

```

@@

```{r Summary of Limitations}

@@

  'Paths_Forward' = c(
    'Flash Plant Species Surveys on Plot', 
    'Develop and Disseminate Education Materials; Herbaria Collections', 
    'Advocate Herbarium Collections', 
    'Plant and Fungal Tree of Life; ', 
    'Posterior-Probabilities; Floral Abundance, Nectar/Pollen Nutrition', 
    'Jaccard Index, Plot Abundance',
    'Spike Samples with Reference Materials; Several Genome Sizes'
  )
)
```

>>>>

---
title: "Conceptual Boxes"
author: "steppe"
date: "2023-03-01"
output:
  pdf_document: default
  html_document: default
---

@@

```{r Applications of metabarcoding in plants, echo = F}

applications <- data.frame(
  'Application' = c(
    'Plant-Animal Interactions',
    'Noxious Weed Detection',
    'Detection of Rare Species', 
    'Forensic Science',
    'Pharmaceutical'
  ),
  'Example' = c(

    'Dietary Preferences of herbivores',
    'Presence of species by hydrologic Basin',
    'Presence of Rare Aquatic Species',
    'Identifying the provenance of materials found at crime scene',
    'Identifying adulterants in wholesale products'
  ),
  'Citation' = c(
    'Soininen et al. 2009',
    'Coghlan et al. 2021',
    'Tsukamoto et al. 2021',
    'Allwood et al. 2020',
    'Bell et al. 2022'
  )
)

write.csv(applications, '../data/Applications_Table.csv', row.names = F)
read.csv('../data/Applications_Table.csv') |>
  knitr::kable(caption = 'Applications of Plant Metabarcoding',
             col.names = c('Application', 'Example', 'Citations'))

rm(applications)
```

@@

```{r Major Issues, echo = F}

bottlenecks <- data.frame(

  'Issue' = c(
    'Taxonomic Resolution',
    'Reference Library - Phylogenetic',
    'Reference Library - Spatial',
    'Reference Library Generation', 
    'Uncertainty with Matches',
    'Species Surrogates',
    'False Positives'
  ),

  'Approach' = c(
    'A353', 
    'Kew PAFTOL, no phylogenetic biases', 
    'Some bias persists towards Europe',
    'Spatial Modelling; Code within', 
    'Temporal Filter System',
    'Temporal Filter System',
    'Spatial & Temporal Modelling, Jaccard Index, high quality reference loci'
  ),

  'Citation' = c(
    c('Coissoc et al. 2016, Kress 2017'),  #taxonomic resolution
    c('Kress 2017, Bell et al. 2022'),  # reference library phylogenetic
    c('Cheng et al. 2018, Darwin Tree of Life 2022, Lewin et al. 2020, Bell et al. 2021'),  # 'Reference Library spatial
    c('Bell et al. 2022'), #  'Reference Library Generation', 
    c('Bell et al. 2022'), #   'Uncertainty with Matches',
    c('?'), #   'Species Surrogates',
    c('Bell et al. 2021') #   'False Positives'
  )
)

write.csv(bottlenecks, '../data/Bottlenecks_Table.csv', row.names = F)

read.csv('../data/Bottlenecks_Table.csv') |>
  knitr::kable(caption = 'Current Issues Facing Plant Metagenomics',
             col.names = c('Issue', 'Our Approach', 'Issue Citation'))

rm(bottlenecks)
```

@@

```{r Summary of Limitations, echo = F}

@@

  'Paths_Forward' = c(
    'Flash Plant Species Surveys on Plot', 
    'Develop and Disseminate Education Materials; Herbaria Collections', 
    'Advocate Herbarium Collections', 
    'Plant and Fungal Tree of Life; 10kP', 
    'Posterior-Probabilities; Floral Abundance, Nectar/Pollen Nutrition', 
    'Jaccard Index, Plot Abundance',
    'Spike Samples with Reference Materials; Several Genome Sizes'
  )
)

write.csv(limitations, '../data/Limitations_Table.csv', row.names = F)

read.csv('../data/Limitations_Table.csv') |>
  knitr::kable(caption = 'Limitations Faced and Possible Solutions',
             col.names = c('Method Component', 'Limitations', 'Paths Forward'))

rm(limitations)
```

### 2023-03-03 script/manuscript_MEE.Rmd
need to check diff, copied in a funny character

--- 
title: Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging Patterns of Queen Bumble Bees
author:  |
    | Reed Clark Benkendorf$^1$$^,$$^2$^[Correspondence: reedbenkendorf2021@u.northwestern.edu], Jane E. Ogilive$^3$$^, Emily J. Woodworth$^1$$^,$$^2$, 
    |  Sophie Taddeo$^1$$^,$$^2$, Paul J. CaraDonna$^1$$^,$$^2$$^,$$^3$, Jeremie B. Fant$^1$$^,$$^2$  
    |  $^1$Chicago Botanic Garden, 1000 Lake Cook Road, Glencoe, Illinois 60022, USA  
    |  $^2$Plant Biology and Conservation, Northwestern University, Evanston, Illinois 60208, USA  
    |  $^3$ Rocky Mountain Biological Laboratory, P.O. Box 519, Crested Butte, Colorado 81224, USA
abstract:  |  
  |  
  1) DNA Barcoding has been successful for the rapid analysis of complex ecological assemblages. Barcoding in the plant kingdom barcoding has been more difficult than in others, and hence may begin to lag behind other kingdoms. 
  2) Here we test the utilization of Angiosperms 353 probes to barcode plant species found in corbiculae pollen loads collected from Queen Bumble Bees. 
  3) To verify the accuracy of this barcoding system we compared the barcoding data to museum plant specimens, observations of plant flowering and bee flower visitation in the field, and species distribution modelling to identify likely candidate plant species found within the corbiculae pollen loads.
  4) By utilizing Species distribution modelling we allow users to create a regionally appropriate sequence databases which may use increase the alignment algorithms minimizing need for large computational power, and run time. 
  5) We show that the Angiosperms 353 probes, developed for phylogenmoics, and which are currently being used in the largest ever plant systematic endeavor, offer significant promise to metagenomic approaches. 
  6) The DNA barcoding of bumble bee corbiculae pollen loads was most accurate when combined with knowledge of what plant species were flowering in the plant community when they were collected. Thus, supplementing DNA barcoding data with ecological context is most accurate and powerful.
keywords: |
  DNA baroding, metagenomics, hyb-seq, Angiosperms353, plant metagenomics, bombus queens, subalpine, species distribution model
output:
  pdf_document: default
  toc: no
  word_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: yes
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---

@@

  r <- paste0('were detected in ',  detected, 
                '% of samples where the proportion of target grains were between ', 
                Lprop, '-', Hprop,  ' (n = ', total, ' Mdn = ', Mdn, ')')
  return(r)
}

@@

The inability to reliably identify plants to terminal taxon can limit our understanding of ecosystem function and interactions (@bortolus2008error). This is especially true for genera where identification down to species can be useful as specific bioindicators; defining ecological and behavioral properties  (e.g. different species of Sagebrush- *Artemisia* L., Willows - *Salix* L., and Sedges - *Carex* L.) (@Gage2013HistoricalRO).In these instances the lack of species level data can hinder our understanding of the breadth of habitat which some species occupy, and their interactions with other species. This can be further complicated by the fact that the identification of organisms to species is also often mired by lack of diagnostic characters(e.g. flowers, fruits, roots or combinations thereof), an increasing lack of taxonomic experts (@hebert2003biological) and the presence of cryptic species (@janzen2017nuclear, @oliver2009cryptic). Taxonomic verification can also be limited by the fact that revisiting field sites to identify material using morphological or chemical approaches, can be resource intensive and often ineffective. The current methods to ameliorate this situation include: (i) ignoring these ecologically relevant levels of detail, (ii) revisiting plots as diagnostic material becomes temporally available, (iii) seeking the assistance from taxonomic specialists, or (iv) the use of barcoding using molecular techniques (CITE).

  Currently the largest plant systematic endeavor ever undertaken,by the Royal Botanic Gardens Kew, the Plant and Fungal Tree of Life (PAFTOL) is approaching completion (@baker2021PAFTOL).  This data set will contain hybridization capture (Hyb-Seq) data from at least one species in each genus of the plant kingdom,14,000 represented species, using the popular Angiosperms353 (A353) probes, which includes 353 single-copy orthologous loci, (@baker2021PAFTOL, @johnson2019universal). These publicly available data serve to provide a taxonomically comprehensive backbone for plant metabarcoding. The A353 probes are currently being used in many other plant phylogenetic studies increasing the sampling depth of many clades  (@baker2021exploring).Data from the 10kP project, which seeks to develop reference genomes from a phylogenetically diverse suite of plants, will contribute many more species by 2030 (@cheng2018tenkp). Similar projects such as the ‘Darwin Tree of Life’ which will sequence all described taxa in Britain and Ireland, seek to sequence high numbers of genomes in geographic regions will contribute data sets applicable to enormous spatial domains (@darwin2022project, @lewin2022biogenome). These data will promote the ability to apply metabarcoding to resolve a diverse array of questions relevant to theoretical and applied ecology (@kress2017plant, @hollingsworth2016telling). However, the application of metabarcoding still faces challenges relating to the enormity of the genomic data sets and the computational power required to process sequence data.

  Herein we have resolved major components of the problems of identifying plant material without diagnostic morphological character states using the A353 Hyb-Seq probes (@johnson2019universal), and custom species sequence databases derived via species distribution modelling, and temporal filtering.

  To increase the quality of metabarcoding results in plants, we are proposing reducing the number of possible candidate species by generating a user specific databases relevant to the region of study and the ecological characteristics of interest (@bell2022plants). To achieve this goal, we first create a regional list of candidate species using digital collections gleaned from herbaria, survey work, and citizen science (e.g. iNaturalist), from a region exceeding the study area. For these candidate species, a modelling approach, such as logistic regression, may be used to identify taxa which warrant further exploration e.g. determine their possibility of presence in metabarcoding samples. We then use species distribution models to create potential distribution maps for the candidate species to limit the impact of spatial and taxonomic biases in the species list and account for spatial variations in niche availability throughout the study area. Species distribution models examine the ecological conditions associated with the known occurrence of a species to identify suitable habitats in the study area. This approach has the benefit of greatly reducing the size of a sequence database, which allows for the use of genomic data on personal computers. This approach can significantly reduce processing time, particularly as most next-generation sequence data is deposited as raw-sequence reads.

  As species interactions vary both in space and time (@~THOMSON1994 GEO?, @caradonna2021seeing). Contrasts in the flowering periods of many plant species, can provide an additional filter for identifying material in certain types of metagenomic samples (@janzen1967synchronization, @Newstrom1994ANC). In high elevation temperate regions, pollination interactions vary temporally and are characterized by high turnover in active periods of species (@caradonna2017interaction), however the overall shorter extent of the active growing season in these systems results in the presence of few to any natural breaks,  which reduces the utility of these to operate as filters in the post-processing of sequence matches. Nonetheless, we work develop a general approach which seems applicable to many areas which utilize the temporal dimension for classifying sequences in metagenomic samples (but see @davis2022new).

  We tested this metagenomic and informatics approach to determine to examine the foraging behaviour of queen bumblebee, and compare this approach with direct observations and the pollen record, which has shown some incongruency in several floral visitation networks involving smaller bodied fauna (@barker2021pollen, @zhao2019topology, @alarcon2010congruence). The assessment of the plant species compositions from pollen is a desirable approach, with several potential applications, despite numerous potential complications (@pornon2017dna, @bell2017applying, @sickel2015increased, @bell2019quantitative, @suchan2019pollen,  @johnson2021airborne). The two foraging phases of the queen bumblebee life cycle are essential to 1) increase their weight before diapause, and 2) increase their ovary weights while establishing their recently found nests. Both of these time periods represent potential demographic bottlenecks in bumble bee populations (@sarro2022bumble, ...). Bumblebees are one of the only groups of insects with unequivocal quantitative evidence for numerous population declines, while simultaneously serving as the most effective pollinators in many temperate montane ecosystems (@cameron2020global, @goulson2008decline, @williams1982distribution, @colla2012assessing, @bergman1996micrometeorological, @bingham1998efficient, @grixti2009decline). These areas often represent the most diverse areas in the temperate and often offer the sole potential refugia for multiple dimensions of biodiversity under climate change, whilst simultaneously experiencing the greatest proportional changes in mean annual temperature (@brito2018climate, @pepin2022climate). An immediate understanding of how to manage previously overlooked keystone insect species, such as bumble bees, is essential if the refugial potential of the temperate mountains are to be incorporated into their current diversity (@loarie2009velocity, @dobrowski2016climate).

@ogilvie2022shifting

@@

Bee and flower observations and bee corbiculae pollen collection was conducted around the Rocky Mountain Biological Laboratory (RMBL; 38°57.5” N, 106°59.3” W (WGS 84), 2900 m.a.s.l.), Colorado, USA (APPENDIX 1 for site information). The area is characterized by subalpine meadow vegetation communities. Pollinator observations of Bombus Latreille spp. (Apidae Latreille) were conducted from May 29th – July 23rd of 2015 in six study sites as a part of a larger study (described in Ogilvie and CaraDonna 2022). Observations of Bombus foraging took place for one hour at each field site, with equal time spent searching for bee in the major vegetation types (dry, and wet meadows, and aspen forest). Corbiculae pollens loads were, non-lethally, collected from queens encountered by capturing them in an insect net and transferring them into a restraining device (“bee squeezer”, @kearns2001natural). We then collected a single pollen load (i.e., from one leg) from the bee and then released it. At weekly intervals at each site, we also recorded the abundances of flowers visited by bumble bees within belt transects spread over the three vegetation types (0.5 x 40 m transects in each vegetation type, 60 m^2^ total area per site).

@@

@@

```{r Molecular Networks, echo = F, out.width="110%"}
knitr::include_graphics('../graphics/plots/Molecular_nets.pdf')
```

>>>>

--- 
title: Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging Patterns of Queen Bumble Bees
author:  |
    | Reed Clark Benkendorf$^1$$^,$$^2$^[Correspondence: reedbenkendorf2021@u.northwestern.edu], Jane E. Ogilive^$$^3$^, Emily J. Woodworth$^1$$^,$$^2$, 
    |  Sophie Taddeo$^1$$^,$$^2$, Paul J. CaraDonna$^1$$^,$$^2$$^,$$^3$, Jeremie B. Fant$^1$$^,$$^2$  
    |  $^1$Chicago Botanic Garden, 1000 Lake Cook Road, Glencoe, Illinois 60022, USA  
    |  $^2$Plant Biology and Conservation, Northwestern University, Evanston, Illinois 60208, USA  
    |  $^3$ Rocky Mountain Biological Laboratory, P.O. Box 519, Crested Butte, Colorado 81224, USA
abstract:  |  
  1) DNA Barcoding has been successful for the rapid analysis of complex ecological assemblages. Barcoding in the plant kingdom barcoding has been more difficult than in others, and hence may begin to lag behind other kingdoms. 
  2) Here we test the utilization of Angiosperms 353 probes to barcode plant species found in corbiculae pollen loads collected from Queen Bumble Bees. 
  3) To verify the accuracy of this barcoding system we compared the barcoding data to museum plant specimens, observations of plant flowering and bee flower visitation in the field, and species distribution modelling to identify likely candidate plant species found within the corbiculae pollen loads.
  4) By utilizing Species distribution modelling we allow users to create a regionally appropriate sequence databases which may use increase the alignment algorithms minimizing need for large computational power, and run time. 
  5) We show that the Angiosperms 353 probes, developed for phylogenmoics, and which are currently being used in the largest ever plant systematic endeavor, offer significant promise to metagenomic approaches. 
  6) The DNA barcoding of bumble bee corbiculae pollen loads was most accurate when combined with knowledge of what plant species were flowering in the plant community when they were collected. Thus, supplementing DNA barcoding data with ecological context is most accurate and powerful.
keywords: |
  DNA baroding, metagenomics, hyb-seq, Angiosperms353, plant metagenomics, bombus queens, subalpine, species distribution model
output:
  pdf_document: default
  toc: no
  word_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: yes
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---

@@

  r <- paste0('were detected in ',  detected, 
                '% of samples where the proportion of target grains were between ', 
                Lprop, '-', Hprop,  ' (n = ', total, ' Mdn = ', Mdn, ')')
  return(r)
}
```

@@

The inability to reliably identify plants to terminal taxon can limit our understanding of ecosystem function and interactions (@bortolus2008error). This is especially true for genera where identification down to species can be useful as specific bioindicators; defining ecological and behavioral properties  (e.g. different species of Sagebrush- *Artemisia* L., Willows - *Salix* L., and Sedges - *Carex* L.) (@Gage2013HistoricalRO). In these instances the lack of species level data can hinder our understanding of the breadth of habitat which some species occupy, and their interactions with other species. This can be further complicated by the fact that the identification of organisms to species is also often mired by lack of diagnostic characters(e.g. flowers, fruits, roots or combinations thereof), an increasing lack of taxonomic experts (@hebert2003biological) and the presence of cryptic species (@janzen2017nuclear, @oliver2009cryptic). Taxonomic verification can also be limited by the fact that revisiting field sites to identify material using morphological or chemical approaches, can be resource intensive and often ineffective. The current methods to ameliorate this situation include: (i) ignoring these ecologically relevant levels of detail, (ii) revisiting plots as diagnostic material becomes temporally available, (iii) seeking the assistance from taxonomic specialists, or (iv) the use of barcoding using molecular techniques (@hebert2003biological).

  Recently barcoding (the identification of a sample from a single organism *e.g.* a piece of leaf), and metabarcoding (the identification of a sample containing a mix of organisms *e.g.* soil), have shown considerable promise in all Kingdoms of Life (@ruppert2019past). With plants the identification of members of certain clades using barcoding has been quite successful (@kress2017plant), whereas with many other clades results have been elusive (@liu2014identification, @china2011comparative, @coissac2012bioinformatic), however metabarcoding incurs additional challenges to those which  exist for the currently implemented barcodes (@li2015plant, @kress2007two, @cbol2009dna, @coissac2012bioinformatic). Particular challenges with the high copy number barcodes (e.g. ITS2, *rbcL*, *matK*, *trnH-psbA*) include the utilization their rates of divergence, gene tree conflict, and hybridization (@coissac2016barcodes, @fazekas2009plant). Currently, most plant metabarcoding endeavors only allow the identification of material to the level of family or genus.

```{r Applications of Metabarcoding}
read.csv('../data/Applications_Table.csv') |>
  knitr::kable(caption = 'Applications of Plant Metabarcoding',
             col.names = c('Application', 'Example', 'Citations'))
```

  Currently the largest plant systematic endeavor ever undertaken,by the Royal Botanic Gardens Kew, the Plant and Fungal Tree of Life (PAFTOL) is approaching completion (@baker2021PAFTOL).  This data set will contain hybridization capture (Hyb-Seq) data from at least one species in each genus of the plant kingdom,14,000 represented species, using the popular Angiosperms353 (A353) probes, which includes 353 single-copy orthologous loci, (@baker2021PAFTOL, @johnson2019universal). These publicly available data serve to provide a taxonomically comprehensive backbone for plant metabarcoding. The A353 probes are currently being used in many other plant phylogenetic studies increasing the sampling depth of many clades  (@baker2021exploring). Data from the 10kP project, which seeks to develop reference genomes from a phylogenetically diverse suite of plants, will contribute many more species by 2030 (@cheng2018tenkp). Similar projects such as the ‘Darwin Tree of Life’ which will sequence all described taxa in Britain and Ireland, seek to sequence high numbers of genomes in geographic regions will contribute data sets applicable to enormous spatial domains (@darwin2022project, @lewin2022biogenome). These data will promote the ability to apply metabarcoding to resolve a diverse array of questions relevant to theoretical and applied ecology (@kress2017plant, @hollingsworth2016telling). However, the application of metabarcoding still faces challenges relating to the enormity of the genomic data sets and the computational power required to process sequence data.

  Herein we have resolved major components of the problems of accurately and effectively identifying plant material without diagnostic morphological character states using the A353 Hyb-Seq probes (@johnson2019universal), and custom species sequence databases derived via species distribution modelling, and temporal filtering. To increase the accuracy and efficiency of metabarcoding results in plants, we are proposing reducing the number of possible candidate species by generating a user specific databases relevant to the region of study and the ecological characteristics of interest (@bell2022plants). To achieve this goal, we first create a regional list of candidate species using digital collections gleaned from herbaria, survey work, and citizen science (e.g. iNaturalist), from a region exceeding the study area. For these candidate species, a modelling approach, such as logistic regression, may be used to identify taxa which warrant further exploration e.g. determine their possibility of presence in metabarcoding samples. We then use species distribution models to create potential distribution maps for the candidate species to limit the impact of spatial and taxonomic biases in the species list and account for spatial variations in niche availability throughout the study area. Species distribution models examine the ecological conditions associated with the known occurrence of a species to identify suitable habitats in the study area. This approach has the benefit of greatly reducing the size of a sequence database, which allows for the use of genomic data on personal computers. This approach can significantly reduce processing time, increasing the a projects efficiency, particularly as most next-generation sequence data is deposited as raw-sequence reads.

```{r Current Bottlenecks in Plant Metabarcoding}
read.csv('../data/Bottlenecks_Table.csv') |>
  knitr::kable(caption = 'Current Issues Facing Plant Metagenomics',
             col.names = c('Issue', 'Our Approach', 'Issue Citation'))
```

  As species interactions vary both in space and time (@thompson1994coevolutionary, @caradonna2021seeing). Contrasts in the flowering periods of many plant species, can provide an additional filter for increasing the accuracy of identifying material in certain types of metagenomic samples (@janzen1967synchronization, @Newstrom1994ANC). In high elevation temperate regions, pollination interactions vary temporally and are characterized by high turnover in active periods of species (@caradonna2017interaction), however the overall shorter extent of the active growing season in these systems results in the presence of few to any natural breaks, which reduces the utility of these to operate as filters in the post-processing of sequence matches. Nonetheless, we work develop a general approach which seems applicable to many areas which utilize the temporal dimension for classifying sequences in metagenomic samples (but see @davis2022new).

  We tested this metagenomic and informatics approach to determine to examine the foraging of queen bumblebee, and compare this approach with direct observations and the pollen record, which has shown some incongruency in several floral visitation networks involving smaller bodied fauna (@barker2021pollen, @zhao2019topology, @alarcon2010congruence). The assessment of the plant species compositions from pollen is a desirable approach, with several potential applications, despite numerous potential complications (@pornon2017dna, @bell2017applying, @sickel2015increased, @bell2019quantitative, @suchan2019pollen,  @johnson2021airborne). The two foraging phases of the queen bumblebee life cycle are essential to 1) increase their weight before diapause, and 2) increase their ovary weights while establishing their recently found nests. Both of these time periods represent potential demographic bottlenecks in bumble bee populations (@sarro2022bumble). Bumblebees are one of the only groups of insects with unequivocal quantitative evidence for numerous population declines, while simultaneously serving as the most effective pollinators in many temperate montane ecosystems (@cameron2020global, @goulson2008decline, @williams1982distribution, @colla2012assessing, @bergman1996micrometeorological, @bingham1998efficient, @grixti2009decline). These areas often represent the most diverse areas in the temperate and often offer the sole potential refugia for multiple dimensions of biodiversity under climate change, whilst simultaneously experiencing the greatest proportional changes in mean annual temperature (@brito2018climate, @pepin2022climate). An immediate understanding of how to manage previously overlooked keystone insect species, such as bumble bees, is essential if the refugial potential of the temperate mountains are to be incorporated into their current diversity (@loarie2009velocity, @dobrowski2016climate).

@@

Bee and flower observations and bee corbiculae pollen collection was conducted around the Rocky Mountain Biological Laboratory (RMBL; 38°57.5” N, 106°59.3” W (WGS 84), 2900 m.a.s.l.), Colorado, USA (APPENDIX 1 for site information). The area is characterized by subalpine meadow vegetation communities. Pollinator observations of Bombus Latreille spp. (Apidae Latreille) were conducted from May 29th – July 23rd of 2015 in six study sites as a part of a larger study (described in Ogilvie and CaraDonna 2022). Observations of Bombus foraging took place for one hour at each field site, with equal time spent searching for bee in the major vegetation types (dry, and wet meadows, and aspen forest). Corbiculae pollens loads were, non-lethally, collected from queens encountered by capturing them in an insect net and transferring them into a restraining device ("bee squeezer", @kearns2001natural). We then collected a single pollen load (i.e., from one leg) from the bee and then released it. At weekly intervals at each site, we also recorded the abundances of flowers visited by bumble bees within belt transects spread over the three vegetation types (0.5 x 40 m transects in each vegetation type, 60 m^2^ total area per site).

@@

```{r Table of Limitations Faced}
read.csv('../data/Limitations_Table.csv') |>
  knitr::kable(caption = 'Limitations Faced and Possible Solutions',
             col.names = c('Method Component', 'Limitations', 'Paths Forward')) 
```

@@

```{r Molecular Networks, echo = F, out.width="110%"}
knitr::include_graphics('../graphics/plots/Molecular_nets-crop.pdf')
```
